My title

### 2024-04-04 paper/paper.qmd
update paper
update abstract

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jessica Im
thanks: "Code and data are available at: https://github.com/jimessica/boycott"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.
```{r}
#| label: fig-rawdataNKE
#| fig-cap: Description of Raw Nike Stock Columns and How They Were Cleaned
#| echo: false

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jessica Im
thanks: "Code and data are available at: https://github.com/jimessica/boycott"
date: today
date-format: long
abstract: "Introduction to the topic and its importance. What I did in my research and analysis. What was found from my research and analysis. Significance of my findings."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-rawdataNKE
#| fig-cap: Description of Raw Nike Stock Columns and How They Were Cleaned
#| echo: false
